V1298~Tau with TESS: Updated Ephemerides, Radii, and Period Constraints from a Second Transit of V1298~Tau~e

### 2021-12-21 src/ms.tex
move the figure
no linenumbers for arxiv
version 2

\documentclass[linenumbers,modern,twocolumn]{aastex631}

\include{style}

\submitjournal{AJ}

@@

\sname is a young (20--30~Myr) solar analogue hosting four transiting exoplanets with sizes between $0.5 - 0.9 R_J$. Given the system's youth,  it provides a unique opportunity to understand the evolution of planetary radii at different separations in the same stellar environment. \sname was originally observed 6 years ago during \textit{K2} Campaign 4. Now, \sname has been re-observed during the extended mission of NASA's Transiting Exoplanet Survey Satellite (\tess). Here, we present new photometric observations of \sname from the 10-minute \tess\ Full-Frame Images. We use the \tess\ data to update the ephemerides for \allplanets as well as compare newly observed radii to those derived from the \textit{K2} light curve, finding shallower transits for \planetknown in the redder \tess\ bandpass at the $1-2\sigma$ level. We suspect the difference in radii is due to starspot-crossing events or contamination from nearby faint stars on the same pixels as \sname. We additionally catch a second transit of \planete and present a new method for deriving the marginalized posterior probability of a planet's period from two transits observed years apart. We find the highest probability period for \planete to be in a near 2:1 mean motion resonance with \planetb which, if confirmed, could make \allplanets a 4 planet resonant chain. \sname is the target of several ongoing and future observations. These updated ephemerides will be crucial for accurately recovering transit events and understanding any future Doppler tomographic or transmission spectroscopy signals.

@@

The youth of \sname was initially established on the basis of its strong X-ray emission \citep{Wichmann1996}, high photospheric lithium abundance \citep{Wichmann2000}, and proper motion measurements \citep{frink1997}. An additional recent blind search for co-moving stars using Gaia DR1 astrometry data found \sname was co-moving with 8 other stars \citep[Group 29 in][]{Oh2017}. A kinematic study of the Taurus star-forming region \citet{Luhman2018} used Gaia DR2 data to extended the membership of this group and derived an age of $\sim$~40~Myr. However, more recent analyses based on Gaia EDR3 astrometry suggests \sname may belong to either the D2 or D3 subgroups of Taurus, both of which have estimated ages $\lesssim$10~Myr \citep{gaidos21, Krolikowski2021}. Other studies focused specifically on the \sname system have estimated its age to be 23$\pm$4~Myr from comparison with empirical and theoretical isochrones \citep{David2019b}, or 28$\pm$4~Myr from isochrone fitting to the \citet{Luhman2018} Group 29 membership list given Gaia EDR3 data \citep{johnson21}. While the precise age of \sname remains uncertain, most estimates fall in the 10--40~Myr range and we adopt $t \approx$~20--30~Myr.

Given the system's youth and potential to reveal information about the initial conditions of close-in planetary systems \citep[e.g.][]{Owen2020,Poppenhaeger2021}, \sname has been the target for extensive follow-up observations. These include efforts to constrain planet masses with radial velocities \citep{Beichman2019}, measure the spin-orbit alignments of planet c \citep{Feinstein21} and planet b \citep{johnson21, gaidos21}, measure or constrain atmospheric mass-loss rates for the innermost planets \citep{Schlawin21, Vissapragada21}, and an approved program to study the planetary atmospheres using the James Webb Space Telescope \citep[JWST;][]{Desert2021}.

Here we report on newly acquired \tess\ observations of \sname which help to refine the orbital ephemerides of the transiting planets and enable comparison of the planet sizes inferred from two different telescopes with different bandpasses (\tess\ and \textit{Kepler}). The letter is laid out as follows. We describe the observations and light curve extraction in Section~\ref{sec:observations}. In Section~\ref{sec:analysis}, we present our light curve modeling and method for computing the marginalized posterior probability of a transiting planet's period from two transits observed with a large time gap. In Section~\ref{sec:radii}, we discuss the differences in measured transit parameters between \textit{K2} and \tess\ data and speculate on the causes for different measured radii. We conclude in Section~\ref{sec:conclusions}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t!]
\begin{center}
\includegraphics[width=0.46\textwidth,trim={0.25cm 0 0 0}]{static/TESSaperture.pdf}
\caption{The \tess\ \texttt{tica} FFI target pixel file (TPF) overlaid with a sky image of \sname taken with the Digitized Sky Survey (DSS) r-band. \sname is highlighted by the white circle; nearby sources with \tess\ magnitudes $< 14$ are marked with orange x's. There are two bight nearby sources to \sname. While aperture photometry would be feasible for this system (yellow square), we found fitting three point-spread functions to the brightest stars extracted the cleanest light curve for \sname. \href{https://github.com/afeinstein20/v1298tau_tess/blob/main/src/figures/tpf.py}{\github}} \label{fig:tpf}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

During its Extended Mission Cycle 4, \tess\ is re-observing many of the previous \textit{K2} fields. \sname (TIC 15756231) was observed by \tess\ in Sectors 43 (UT 16 Sep 2021 to UT 12 Oct 2021) at 10-minute cadence within the Full-Frame Images (FFIs). We used the \texttt{tica} \citep{fausnaugh20} software to download calibrated FFIs for Sector 43 and the first orbit of Sector 44, as these FFIs are quickly available after the data is downlinked.

We created light curves from the \texttt{tica}-processed FFIs by modeling the point-spread function (PSF) of \sname and the two nearby bright sources (see Figure~\ref{fig:tpf}), following the PSF modeling routine in \cite{feinstein19}. In summary, we calculated and maximized the likelihood value of seven parameters per each Gaussian: the $x$ and $y$ width, 2D position, amplitude, a rotational term, and a background term. The Gaussian fits are allowed to vary at each time step. Aperture photometry (example square aperture shown in Figure~\ref{fig:tpf}) provided a light curve with more systematics and scatter. We found that modeling the three brightest stars simultaneously, including \sname, with a 2D Gaussian created the least contaminated light curve. Our extracted light curve is shown in the top row of Figure~\ref{fig:transits}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[hbtp]
\begin{center}
\includegraphics[width=\textwidth,trim={0.25cm 0 0 0}]{figures/transits.pdf}
\caption{\sname extracted light curve from the \texttt{tica}-processed full-frame images for all of Sector 43 and the first orbit of Sector 44, with transits of \allplanets highlighted by color. Each subplot contains the raw, normalized \tess\ flux (top) and the GP model removed flux (de-trended flux; bottom). Top row: extracted light curve with over plotted with our best-fit GP model for stellar variability (black). Bottom three rows: zoomed-in regions around the transits present in the \tess\ data. The GP best-fit model is over-plotted on the raw, normalized flux. The best-fit transit models are over-plotted on the de-trended flux. For overlapping transits (sub-panel ``Planets b, c, \& e''), the sum of the transits is blotted in black.} \label{fig:transits}
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

% planet fits
We simultaneously modeled the transits of \allplanets and the stellar variability using the open-source packages \exoplanet \citep{exoplanet2019, exoplanet2021} and \texttt{PyMC3} \citep{Salvatier16}. Transit timings were originally identified using updated ephemerides from \textit{Spitzer} (Livingston et al. in prep) and we account for potential transit timing variations (TTVs) in our model. All other transit parameters (presented in Table~\ref{tab:table}) were initialized using values from \cite{David2019a}. We assumed a quadratic limb darkening law, following the reparameterization described by \cite{kipping13}; this method allows for an efficient and uniform sampling of limb-darkened transit models.

@@

We performed an MCMC sampling fit to each parameter.\footnote{A Jupyter notebook detailing our model can be found \href{https://github.com/afeinstein20/v1298tau\_tess/blob/main/notebooks/TESS\_V1298Tau.ipynb}{here}.} We ran 3 chains with 500 tuning steps and 5000 draws. We discarded the tuning samples from the posterior chains before calculating our best-fit parameters. Our results are presented in Table~\ref{tab:table}, along with our selected priors for each parameter we fit. We verified our chains converged via visual inspection and following the diagnostic provided by \cite{Geweke92}.

@@

\sname (EPIC~210818897) was observed during Campaign 4 of the \textit{K2} mission. There was a single transit of \planete in the original \textit{K2} data, which occurred roughly in the middle of the campaign. Since no other transits were detected, this provides a lower period limit of 36~days. Using the original transit timing from \textit{K2} and this new transit timing from \tess, we developed a new method for constraining the period of \planete. For this analysis, we used the \texttt{EVEREST 2.0} \citep{luger18} version of the \textit{K2} light curve.

@@

First, we de-trended a localized 1-day region around the transit midpoint of \planete in the \textit{K2} and \tess\ light curves, assuming a constant transit depth and allowing the other transit parameters, $\theta$ to vary. Then, we fit a discrete period model, allowing all other transit parameters to vary. We set the GP model to sample over discrete periods ranging from $38 - 60$~days. We fit for $\theta$ assuming a constant transit depth between the \textit{K2} and \tess\ observations. We assumed there is no correlation between the other transit parameters and the period we are fitting for. For each step in our MCMC fit, we compute all possible periods

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[!ht]
\begin{center}
\includegraphics[width=0.45\textwidth,trim={0.25cm 0 0cm 0}]{static/periode.pdf}
\caption{Our calculated posterior probability to constrain the period of \planete using transit timings from \textit{K2} and \tess. We tested discrete periods from $38-60$\,days and find the most likely period to be 45.003~days. The 2:1 resonance (48.28~days) with \planetb is plotted as the dashed vertical line. \href{https://github.com/afeinstein20/v1298tau_tess/blob/main/notebooks/V1298Tau_e.py}{\github}} \label{fig:period_e}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

We find the most likely period of \planete to be 45.003~days, with a median period of $49.184 \pm 6.685$~days. Even at the lower limit, it is unlikely a transit of \planete will occur in the 2\textsuperscript{nd} orbit of Sector 44. This derived period estimate suggests that \planete is in a near 2:1 mean motion resonance with \planetb. If the period of \planete is confirmed to be within the presented range, this could indicate that \allplanets are in nearly 4 planet resonant chain.

Independent ground-based monitoring of the system may be able to observe another transit of the outermost known planet in this system. Using the Transit Service Query Form on the NASA Exoplanet Archive \citep{Akeson2013}, we provide several potential transit midpoint events, given the top 5 most-likely periods for \planete, at the end of Table~\ref{tab:table}.

@@

We compare the differences in transit $R_p/R_\star$ between the \textit{K2} and \tess\ data in Figure~\ref{fig:compare}. We masked regions in the light curve where transits overlapped. The residuals of the \tess\ light curve with our model (color) are plotted as well. For \planetknown, the transit radii are smaller in the \tess\ data, while only the measured radius for \planete is larger in the \tess\ data (Figure~\ref{fig:compare}, bottom panel).

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[!htb]
\begin{center}
\includegraphics[width=\textwidth,trim={0.25cm 0 0 0}]{static/combined_together.pdf}
\caption{Left: Phase-folded \tess\ data (gray) with the new best-fit model (color) compared to the original \textit{K2} data (black). The residuals between the \tess\ data and each fit are shown underneath. Top right: A comparison of measured $R_p/R_\star$ are presented with a 1-to-1 line plotted in black for reference. The transit depths for \planetknown are shallower in the new \tess\ data, while the transit depth for \planete is deeper. Bottom right: The change in $R_p/R_\star$ as a function of pixel for \planetb (left) and \planete (right) overlaid with a sky image of \sname taken with the Digitized Sky Survey (DSS) r-band. We speculate the variation in transit depths could be due to contamination from nearby bright stars or starspot crossing events. \href{https://github.com/afeinstein20/v1298tau_tess/blob/main/src/figures/dilution_check.py}{\github}} \label{fig:compare}
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

A shallower transit depth at redder wavelengths is supported by the dusty outflow model presented in \citep{wang19}, while transits in the optical probe lower atmospheric pressures, resulting in larger transit depths \citep{gao20}. Therefore, the difference in transit depths could be due to the difference in bandpass wavelength coverage between \textit{Kepler} \citep[400-900~nm;][]{Howell2014} and \tess\ \citep[600-1000~nm;][]{Ricker2015}.

@@

However, it is more likely we are seeing either contamination/dilution from another nearby star or the presence of starspots. As highlighted in Figure~\ref{fig:tpf}, there is a bright (\tess\ magnitude $<$ 14) just next to \sname. Since we did not include this source in our light curve PSF-modeling, it is possible there is some light from this source in our data, therefore making the transits of \planetknown appear $\sim 10$\% shallower in our \tess\ data than the original \textit{K2} measurements. The \tess\ Input Catalog \citep{stassun18} lists a contamination value of 0.315 for \sname, which could sufficiently produce the decrease in transit depths presented here.

We check for signs of dilution by creating light curves for individual pixels around \sname and measure the transit depths of \planetb and \planete (Figure~\ref{fig:compare}). We localized a 1-day window around each transit and computed the a $\chi^2$ fit using a transit model computed with \texttt{batman} \citep{Kreidberg15} and an underlying 2\textsuperscript{nd} order polynomial. We find the transit depths to decrease falling off of the pixels centered on \sname. While fitting the \tess\ PSF with a 2D Gaussian function is a reasonable approximation, it is not the perfect model. It is possible that this light curve is diluted from nearby stars, including TIC~15756226, which is the closest (separation $= 49.15\arcsec$) star with $T_\textrm{mag} = 13.09$.

@@

We present new ephemerides for all four known planets in the \sname system. We detected a second transit of \planete; this new transit time in combination from the transit observed with \textit{K2} allowed us to place tighter constraints on the period of the outermost planet. Our revised radius for planet e makes it now the largest planet in the system and extends an intriguing size--separation correlation in \sname such that planet size increases monotonically with separation.

@@

The youth of these planets could additionally favor hosting haze-dominated atmospheres. However, without mass estimates for \allplanets, it is difficult to determine if this is the cause of the different transit depths measured between the \textit{K2} data and our presented work. Radial velocity mass measurements are challenging for young planets due to underlying stellar activity. A more promising approach to measuring the masses would be through TTVs \citep{agol18}. A full TTV analysis \textit{K2}, \textit{Spitzer}, and \tess\ transit photometry is presented in Livingston et al. (in prep). Additional transits at longer wavelengths or simultaneous multi-band photometry or spectroscopy could corroborate the potential of constraining the properties of these young atmospheres.

%The Python code used to access the data, process and model the light curve, and reproduce the tables and figures are made publicly available.\footnote{\url{https://github.com/afeinstein20/v1298tau_tess}}

\begin{acknowledgments}
We thank Rodrigo Luger for developing \texttt{showyourwork!} \citep{luger21} and helping us debug this letter, and we thank Chas Beichman and Sarah Blunt for helpful comments on our \tess\ proposal (DDT 036). ADF acknowledges support from the National Science Foundation Graduate Research Fellowship Program under Grant No. (DGE-1746045).

@@

$P_{rot}$ [days] & $2.97_{-0.04}^{+0.03}$ & $\mathcal{G}($ln$ 2.87, 2)$ & & \\

@@

ln($\sigma_l$) & $-2.499_{-4.463}^{+4.444}$ & $\mathcal{G}($ln$(0.1\sigma_\textrm{flux}), 10)$ & & \\

>>>>

\documentclass[linenumbers,twocolumn]{aastex631}

\usepackage{xspace}

\usepackage{xcolor, fontawesome}
\definecolor{twitterblue}{RGB}{64,153,255}

\newcommand{\twitter}[1]{\href{https://twitter.com/#1}{\textcolor{twitterblue}{\faTwitter}\,\tt \textcolor{twitterblue}{@#1}}}

\newcommand{\github}[1]{\href{https://github.com/#1}{\textcolor{black}{\faGithub}\,\tt \textcolor{black}{#1}}}

\newcommand{\githubicon}{{\color{black}\faGithub}}

\newcommand{\tess}{\textit{TESS}}
\newcommand{\sname}{V1298~Tau\xspace}
\newcommand{\allplanets}{V1298~Tau~bcde\xspace}
\newcommand{\planetb}{V1298~Tau~b\xspace}
\newcommand{\planetc}{V1298~Tau~c\xspace}
\newcommand{\planetd}{V1298~Tau~d\xspace}
\newcommand{\planete}{V1298~Tau~e\xspace}
\newcommand{\planetknown}{V1298~Tau~bcd\xspace}
\newcommand{\rearth}{$R_\oplus$\xspace}
\newcommand{\exoplanet}{\texttt{exoplanet}\xspace}

\submitjournal{ApJL}

@@

\sname is a young (20--30~Myr) solar-mass K star hosting four transiting exoplanets with sizes between $0.5 - 0.9 R_J$. Given the system's youth,  it provides a unique opportunity to understand the evolution of planetary radii at different separations in the same stellar environment. \sname was originally observed 6 years ago during \textit{K2} Campaign 4. Now, \sname has been re-observed during the extended mission of NASA's Transiting Exoplanet Survey Satellite (\tess). Here, we present new photometric observations of \sname from the 10-minute \tess\ Full-Frame Images. We use the \tess\ data to update the ephemerides for \allplanets as well as compare newly observed radii to those measured from the \textit{K2} light curve, finding shallower transits for \planetknown in the redder \tess\ bandpass at the $1-2\sigma$ level. We suspect the difference in radii is due to starspot-crossing events or contamination from nearby faint stars on the same pixels as \sname. Additionally, we catch a second transit of \planete and present a new method for deriving the marginalized posterior probability of a planet's period from two transits observed years apart. We find the highest probability period for \planete to be in a near 2:1 mean motion resonance with \planetb which, if confirmed, could make \allplanets a 4 planet resonant chain. \sname is the target of several ongoing and future observations. These updated ephemerides will be crucial for scheduling future transit observations and interpreting future Doppler tomographic or transmission spectroscopy signals.

@@

The youth of \sname was initially established on the basis of its strong X-ray emission \citep{Wichmann1996}, high photospheric lithium abundance \citep{Wichmann2000}, and proper motion measurements \citep{frink1997}. An additional recent blind search for co-moving stars using Gaia DR1 astrometry data found \sname was co-moving with 8 other stars \citep[Group 29 in][]{Oh2017}. \cite{Luhman2018} conducted a kinematic study of the Taurus star-forming region using Gaia DR2 and found new members of this group. With this new sample, they derived an age of $\sim$~40~Myr. However, more recent analyses based on Gaia EDR3 astrometry suggests \sname may belong to either the D2 or D3 subgroups of Taurus, both of which have estimated ages $\lesssim$10~Myr \citep{gaidos21, Krolikowski2021}. Other studies focused specifically on the \sname system have estimated its age to be 23$\pm$4~Myr from comparison with empirical and theoretical isochrones \citep{David2019b}, or 28$\pm$4~Myr from isochrone fitting to the \citet{Luhman2018} Group 29 membership list given Gaia EDR3 data \citep{johnson21}. While the precise age of \sname remains uncertain, most estimates fall in the 10--40~Myr range and we adopt $t \approx$~20--30~Myr.

Given the system's youth and potential to reveal information about the initial conditions of close-in planetary systems \citep[e.g.][]{Owen2020,Poppenhaeger2021}, \sname has been the target for extensive follow-up observations. These include efforts to constrain planet masses with radial velocities \citep{Beichman2019,suarez21}, measure the spin-orbit alignments of planet c \citep{Feinstein21} and planet b \citep{johnson21, gaidos21}, measure or constrain atmospheric mass-loss rates for the innermost planets \citep{Schlawin21, Vissapragada21}, and an approved program to study the planetary atmospheres using the James Webb Space Telescope \citep[JWST;][]{Desert2021}.

Here we report on newly acquired \tess\ observations of \sname which help to refine the orbital ephemerides of the transiting planets and enable comparison of the planet sizes inferred from two different telescopes with different bandpasses (\tess\ and \textit{Kepler}). The goal of this letter is to provide a quick analysis of the new \tess\ data to help improve the transit timings for follow-up observations being performed by the community. We describe the observations and light curve extraction in Section~\ref{sec:observations}. In Section~\ref{sec:analysis}, we present our light curve modeling and method for computing the marginalized posterior probability of a transiting planet's period from two transits observed with a large time gap. In Section~\ref{sec:radii}, we discuss the differences in measured transit parameters between \textit{K2} and \tess\ data. We conclude in Section~\ref{sec:conclusions}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t!]
\begin{center}
\includegraphics[width=0.46\textwidth,trim={0.25cm 0 0 0}]{static/TESSaperture.pdf}
\caption{The \tess\ \texttt{tica} FFI target pixel file (TPF) overlaid with a sky image of \sname taken with the Digitized Sky Survey (DSS) r-band. \sname is highlighted by the white circle; nearby sources with \tess\ magnitudes $< 14$ are marked with x's. The two stars with white x's (TICs 15756226 and 15756240) were simultaneously fit during our PSF-modeling. The one star with black x (TIC 15756236) is a bright nearby source that was not included in our PSF-modeling. While aperture photometry would be feasible for this system (yellow square), we found fitting three point-spread functions to the brightest stars extracted the cleanest light curve for \sname. \href{https://github.com/afeinstein20/v1298tau\_tess/blob/main/src/figures/tpf.py}{\githubicon}} \label{fig:tpf}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

During its Extended Mission Cycle 4, \tess\ is re-observing many of the previous \textit{K2} fields. \sname (TIC 15756231) was observed by \tess\ in Sectors 43 (UT 16 Sep 2021 to UT 12 Oct 2021) and 44 (UT 12 Oct 2021 to UT 06 Nov 2021). For Sectors 43 and 44, we used the 2-minute light curve created by the Science Processing Operations Center pipeline \citep[SPOC;][]{jenkinsSPOC2016} and binned the data down to 10-minute cadence.% For Sector 44,} we used the \texttt{tica} \citep{fausnaugh20} software to download calibrated Full-Frame Images (FFIs), as these FFIs are quickly available after the data is downlinked.

We compared these new light curves to our original FFI light curves. We created our initial light curves from the \texttt{tica}-processed FFIs by modeling the point-spread function (PSF) of \sname and the two nearby bright sources (white x's in Figure~\ref{fig:tpf}), following the PSF modeling routine in \cite{feinstein19}.\footnote{Our PSF-modeled light curves are available \href{https://github.com/afeinstein20/v1298tau_tess/tree/main/lightcurves}{here}.} In summary, we calculated and maximized the likelihood value of seven parameters per each Gaussian: the $x$ and $y$ width, 2D position, amplitude, a rotational term, and a background term. The Gaussian fits are allowed to vary at each time step. Aperture photometry (example square aperture shown in Figure~\ref{fig:tpf}) provided a light curve with more systematics and scatter. We found that modeling the three brightest stars simultaneously, including \sname, with a 2D Gaussian created the least contaminated light curve. Our extracted light curve is shown in the top row of Figure~\ref{fig:transits}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[hbtp]
\begin{center}
\includegraphics[width=0.9\textwidth,trim={0.25cm 0 0 0}]{figures/transits.pdf}
\caption{\sname extracted light curve from the SPOC-processed light curve for Sectors 43 and 44, with transits of \allplanets highlighted by color. Each subplot contains the raw, normalized \tess\ flux (top) and the GP model removed flux (de-trended flux; bottom). Top row: extracted light curve with over plotted with our best-fit GP model for stellar variability (black). Bottom three rows: zoomed-in regions around the transits present in the \tess\ data. The GP best-fit model is over-plotted on the raw, normalized flux. The best-fit transit models are over-plotted on the de-trended flux. For overlapping transits (sub-panel ``Planets b, c, \& e''), the sum of the transits is blotted in black.} \label{fig:transits}
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

% planet fits
We simultaneously modeled the transits of \allplanets and the stellar variability using the open-source packages \exoplanet \citep{exoplanet2019, exoplanet2021} and \texttt{PyMC3} \citep{Salvatier16}. Transit timings were originally identified using updated ephemerides from \textit{Spitzer} (Livingston et al. in prep) and we account for potential transit timing variations (TTVs) in our model using \texttt{exoplanet}'s \texttt{TTVOrbit} function. This functionality allows us to fit the individual transit time per each transit, while all other orbital and planetary parameters remain the same.

\texttt{exoplanet.TTVOrbit} worked well when fitting \planetknown, due to there being multiple transits. For \planete, we found the GP model with TTVs optimized around hyperparameters that accommodated transits where there were none; as such, we used a model without accounting for TTVs to fit the parameters for \planete. All other transit parameters (presented in Table~\ref{tab:table}) were initialized using values from \cite{David2019a}. We assumed a quadratic limb darkening law, following the reparameterization described by \cite{kipping13}; this method allows for an efficient and uniform sampling of limb-darkened transit models.

@@

We performed an MCMC sampling fit to each parameter.\footnote{A Jupyter notebook detailing our model can be found \href{https://github.com/afeinstein20/v1298tau\_tess/blob/main/notebooks/TESS\_V1298Tau.ipynb}{here}.} We ran 3 chains with 500 tuning steps and 5000 draws. We discarded the tuning samples from the posterior chains before calculating our best-fit parameters. Our results are presented in Table~\ref{tab:table}, along with our selected priors for each parameter we fit. These results are consistent with our original \texttt{tica}-processed point-spread function modeled light curves. We verified our chains converged via visual inspection and following the diagnostic provided by \cite{Geweke92}.

@@

\sname (EPIC~210818897) was observed during Campaign 4 of the \textit{K2} mission. There was a single transit of \planete in the original \textit{K2} data, which occurred roughly in the middle of the campaign. Since no other transits were detected, this provides a lower period limit of 36~days. Additionally, there was only 1 transit of \planete between the two \tess\ sectors, which provides a new lower limit of 42.7~days. Using the original transit timing from \textit{K2} and this new transit timing from \tess, we developed a new method for constraining the period of \planete. For this analysis, we used the \texttt{EVEREST 2.0} \citep{luger18} version of the \textit{K2} light curve.

@@

First, we de-trended a localized 1-day region around the transit midpoint of \planete in the \textit{K2} and \tess\ light curves, assuming a constant transit depth and allowing the other transit parameters, $\theta$ to vary. Then, we fit a discrete period model, allowing all other transit parameters to vary. We set the GP model to sample over discrete periods ranging from $38 - 56$~days. We fit for $\theta$ assuming a constant transit depth between the \textit{K2} and \tess\ observations. We assumed there is no correlation between the other transit parameters and the period we are fitting for. For each step in our MCMC fit, we compute all possible periods

@@

We find the most likely period of \planete to be 44.17~days. We provide all tested periods and posterior probabilities in Table~\ref{tab:e}. Our period estimate is at a 4-$\sigma$ disagreement with the period measured in a potential radial velocity signal for \planete presented in \cite{suarez21}. This derived period estimate suggests that \planete is in a near 2:1 mean motion resonance with \planetb. If the period of \planete is confirmed to be within the presented range, this could indicate that \allplanets are in a nearly 4-planet resonant chain.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[h]
\begin{center}
\includegraphics[width=0.44\textwidth,trim={0.25cm 0 0cm 0}]{figures/periode.pdf}
\caption{Our calculated posterior probability to constrain the period of \planete using transit timings from \textit{K2} and \tess. We tested discrete periods from $q=38-56$\,days and find the most likely period to be 44.17~days. The 2:1 resonance (48.28~days) with \planetb is plotted as the dashed vertical line. \href{https://github.com/afeinstein20/v1298tau\_tess/blob/main/src/figures/period\_e.py}{\githubicon}} \label{fig:period_e}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Independent ground-based monitoring of the system may be able to observe another transit of the outermost known planet in this system. Using the Transit Service Query Form on the NASA Exoplanet Archive \citep{Akeson2013}, we provide several potential transit midpoint events for all fitted periods in Table~\ref{tab:e}.

@@

We compare the differences in transit $R_p/R_\star$ between the \textit{K2} and \tess\ data in Figure~\ref{fig:compare}. We masked regions in the light curve where transits overlapped. The residuals of the \tess\ light curve with our model (color) are plotted as well. For \planetknown, the transit radii are smaller in the \tess\ data, while only the measured radius for \planete is larger (Figure~\ref{fig:compare}, bottom panel).

The error bars from our MCMC fit on the radii of the planets are smaller than that provided by \cite{David2019b}. We initialized our MCMC to fit the transit depths with a Gaussian distribution around the fitted values from \cite{David2019b} with a standard deviation of 0.1 (Table~\ref{tab:table}). The smaller errors could be due to the higher cadence of the \tess\ data (10-minutes vs. 30-minutes) or due to larger spot-crossing events in \textit{K2}. Larger spot-crossings would result in a greater uncertainty of the transit depth, and this is potentially evident in comparing the transit depth and shape for \planete (Figure~\ref{fig:compare}).

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[!htb]
\begin{center}
\includegraphics[width=\textwidth,trim={0.25cm 0 0 0}]{static/compare_together.pdf}
\caption{Left: Phase-folded \tess\ data (gray) with the new best-fit model (color) compared to the original \textit{K2} data (black). The residuals between the \tess\ data and each fit are shown underneath. Top right: The percent difference in measured $R_p/R_\star$ from \textit{K2} vs. \tess\ $R_p/R_\star$. A dashed line is shown at 0\% to help visually differentiate between measured increases and decreases in planetary radii. The transit depths for \planetknown are shallower in the new \tess\ data, while the transit depth for \planete is deeper. Bottom right: The change in $R_p/R_\star$ as a function of pixel for \planetb (left) and \planete (right) overlaid with a sky image of \sname taken with the Digitized Sky Survey (DSS) r-band. We speculate the variation in transit depths could be due to contamination from nearby bright stars or starspot crossing events. \href{https://github.com/afeinstein20/v1298tau_tess/blob/main/src/figures/dilution_check.py}{\githubicon}} \label{fig:compare}
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

A shallower transit depth at redder wavelengths is supported by the dusty outflow model presented in \cite{wang19}, while transits in the optical probe lower atmospheric pressures, resulting in larger transit depths \citep{gao20}. Therefore, the difference in transit depths could be due to the difference in bandpass wavelength coverage between \textit{Kepler} \citep[400-900~nm;][]{Howell2014} and \tess\ \citep[600-1000~nm;][]{Ricker2015}.

@@

However, it is more likely we are seeing either contamination/dilution from another nearby star or the presence of starspots. As highlighted by a black x in Figure~\ref{fig:tpf}, there is a bright (\tess\ magnitude $<$ 14) just next to \sname. Since we did not include this source in our light curve PSF-modeling, it is possible there is some light from this source in our data, therefore making the transits of \planetknown appear $\sim 10$\% shallower in our \tess\ data than the original \textit{K2} measurements. The \tess\ Input Catalog \citep{stassun18} lists a contamination value of 0.315 for \sname, which could sufficiently produce the decrease in transit depths presented here.

We check for signs of dilution by creating light curves for individual pixels around \sname and measure the transit depths of \planetb and \planete (Figure~\ref{fig:compare}). We localized a 1-day window around each transit and computed the a $\chi^2$-fit using a transit model computed with \texttt{batman} \citep{Kreidberg15} and an underlying 2\textsuperscript{nd} order polynomial. We find the transit depths to decrease falling off of the pixels centered on \sname. While fitting the \tess\ PSF with a 2D Gaussian function is a reasonable approximation, it is not the perfect model. It is possible that this light curve is diluted from nearby stars, including TIC~15756226, which is the closest (separation $= 49.15\arcsec$) star with $T_\textrm{mag} = 13.09$.

@@

We present updated ephemerides for all four known planets in the \sname system. Our GP model accounts for TTVs for \planetknown. The transit timings for \planetc deviates from a linear ephemeris by -30 to 30 minutes, and \planetd deviates by -5 to 5 minutes. Additionally, we note the transits of \planetknown occur 1.92 later, and 5.83 and 4.72 hours earlier than what is expected if we extrapolate forward the ephemerides from \cite{David2019b}.

We detected a second transit of \planete; this new transit time in combination from the transit observed with \textit{K2} allowed us to place tighter constraints on the period of the outermost planet. Our revised radius for planet e makes it now the largest planet in the system and extends an intriguing size--separation correlation in \sname such that planet size increases monotonically with separation.

@@

The youth of these planets could additionally favor hosting haze-dominated atmospheres. However, without mass estimates for \allplanets, it is difficult to determine if this is the cause of the different transit depths measured between the \textit{K2} data and our presented work. Radial velocity mass measurements are challenging for young planets due to underlying stellar activity.

Through an intensive radial velocity campaign, \cite{suarez21} presented a new mass detection for \planetb and \planete. Our updated radius estimate for \planetb in combination with the mass estimate provided by \cite{suarez21} would yield a density of $1.29$~g/cm\textsuperscript{3}, which is slightly higher than what was originally reported. Our updated radius for \planete would yield a lower density of $2.04$~g/cm\textsuperscript{3}, which is still within a 1-$\sigma$ agreement with \cite{suarez21}. However, the period estimate for \planete is at a 4-$\sigma$ disagreement for the period estimate provided in this study and at a 2-$\sigma$ disagreement with the minimum period constraint provided by this new \tess\ data.}

A more promising approach to measuring the masses would be through TTVs \citep{agol18}. A full analysis of system parameters and TTVs from both the \textit{K2} and \tess\ light curves, and additional \textit{Spitzer} transit photometry will be presented in Livingston et al. (in prep). Additional transits at longer wavelengths or simultaneous multi-band photometry or spectroscopy could corroborate the potential of constraining the properties of these young atmospheres.

\begin{acknowledgments}
We thank Rodrigo Luger for developing \texttt{showyourwork!} \citep{luger21} and helping us debug this letter. We thank Chas Beichman, Sarah Blunt, Jacob Bean, and Darryl Seligman for helpful comments on our \tess\ proposal (DDT 036) and thoughtful conversations. We thank our anonymous referee for their thoughtful insights which improved the quality of this manuscript. ADF acknowledges support from the National Science Foundation Graduate Research Fellowship Program under Grant No. (DGE-1746045).

@@

$P_{rot}$ [days] & $2.97_{-0.04}^{+0.03}$ & $\mathcal{G}(\textrm{ln} 2.87, 2)$ & & \\

@@

ln($\sigma_l$) & $-2.499_{-4.463}^{+4.444}$ & $\mathcal{G}(ln(0.1\sigma_\textrm{flux}), 10)$ & & \\
